Data Recovery and Pulse Position Modulation with a Photon Number Resolving SNSPD

### 2023-09-23 manuscript.tex
overleaf update

\begin{abstract*} 
Photon number resolution is an emerging capability of advanced Superconducting Nanowire Single Photon Detectors. If leveraged to it's full potential, PNR capability can have a profound impact on the usefulness of SNSPDs is certain quantum applications including linear optical quantum computing, quantum networks, and quantum sensing. Discrimination of not just the number of photons in an optical pulse but also pulse arrival time with high accuracy is an open problem, complicated by the nuanced way in which these two degrees of freedom are intertwined in the response function of these detectors. In this work we put a differential readout SNSPD to the ultimate test. We test it's capabilities in a Pulse Position Modulation experiment whereby data is sent in the arrival time of optical pulses derived from a 20~GHz optical clock. We show the detector is capable of discriminating the arrival time of photons to 50~ps wide bins with high accuracy while simultaneously providing photon number information about the impinging optical pulses. We find that a careful statistical analysis of the PNR response is necessary to back-out a precise measurement of pulse arrival time.
\end{abstract*}

@@

@@

\begin{itemize}
\tightlist
\item
  Efficiency = 0.84
\item
  Afterpulsing = 0 \%
\item
  Jitter = 15 ps
\item
  Deadtime = 30 ns \textcolor{red}{measure 3dB flux}
\item
  Area = 330 \(\mu m^2\)
\item
  Dark count rate = 20\Hz
\end{itemize}

@@

This is the methods section with some latex \(\frac{33}{44}\)

Here is citation \cite{Dolinar2011Photon} and here is the rest of the sentence.

>>>>

\begin{abstract*} 
Photon number resolution is an emerging capability of advanced Superconducting Nanowire Single Photon Detectors. If leveraged to it's full potential, PNR capability can have a profound impact on the usefulness of SNSPDs is certain quantum applications including linear optical quantum computing, quantum networks, and quantum sensing. Discrimination of not just the number of photons in an optical pulse but also pulse arrival time with high accuracy is an open problem, complicated by the nuanced way in which these two degrees of freedom are intertwined in the response function of these detectors. In this work we test a differential readout SNSPD in a Pulse Position Modulation experiment whereby data is sent in the arrival time of optical pulses derived from a 20~GHz optical clock. We show the detector is capable of discriminating the arrival time of photons to 50~ps wide bins with high accuracy while simultaneously providing photon number information about the impinging optical pulses. We find that cluster analysis and gaussian mixture models are useful for extracting precise measurements of pulse arrival time and photon number.
\end{abstract*}

@@

\hypertarget{fig:figurename2}{%
\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{./figs_03/fig_intro_light.pdf}
\caption[{PPM modulation and experiment setup}]{\textbf{PPM modulation and experiment setup} a) How bits are transmitted in M=16 PPM modulation. An optical pulse is transmitted with a clock-referenced integer delay which encodes 4 bits of data. b) Diagram of the expiremental setup. WG: wave generator, CD: clock divider board, AWG: Arbitrary Waveform Generator, MLL: Mode Locked Laser (Pritel UAC), IM: Intensity Modulator, BC: Bias Controller, FSC: Free Space Coupling System, DCA: DC Coupled Cryo-amp}
\label{fig:figurename2}
\end{figure}
}

@@

\begin{itemize}
\tightlist
\item
  Efficiency = 0.84
\item
  Afterpulsing = 0 \%
\item
  Jitter = 15 ps
\item
  Deadtime = 30 ns \textcolor{red}{measure 3dB flux}
\item
  Area = 330 \(\mu m^2\)
\item
  Dark count rate = 20~Hz
\end{itemize}

@@
